---
title: "B-ALL Validation Screen"
author: "Charlie Whittaker"
date: "3/3/2023"
output: 
  html_document:
    toc: true
    toc_depth: 3
  html_notebook: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(tidy=FALSE, cache=TRUE,
                      dev="png", message=FALSE, error=FALSE, warning=TRUE)
```

# Load libraries

```{r, warning=FALSE,error=FALSE,message=FALSE}
library(openxlsx)
library(ggplot2)
library(tidyverse)
library(reprex)
library(matrixStats)
library(XML)
library(ggrepel)
library(ggVennDiagram)
library(GGally)
library(DESeq2)
library(apeglm)
library(ComplexHeatmap)
library(dplyr)
library(readxl)
library(readr)
library(tximport)
library(edgeR)
library(MAGeCKFlute)
library(clusterProfiler)
library(ggpubr)
library(gprofiler2)
library(VennDiagram)
library(clusterProfiler)
library(AnnotationDbi)
library(org.Mm.eg.db)
library(extrafont)
loadfonts(device = "win")
```

# Useful functions

```{r}
vlnplot_essentials <- function(df){
  Essential.toPlot <- merge(x=df, y=essentialGenes, by.x="id" ,by.y="MGISym", all.x=TRUE)
  Essential.toPlot <- Essential.toPlot %>% mutate(Essential = ifelse(is.na(Essential), "No", Essential))
  Essential.toPlot <- Essential.toPlot %>% rename(LFC = Score)
  data <- Essential.toPlot
  plot <- ggplot(data, aes(factor(Essential), LFC)) + geom_violin(fill='#A4A4A4') + geom_boxplot(width=.1) + ylim(-2.5, 2.5) +
    theme_bw() + 
    theme(plot.title = element_text(size = 8),axis.title.x = element_text(size = 8),axis.title.y = element_text(size = 8))
  return(plot)
}
```

# Importing data

## Import from Broad PoolQ count files

```{r}
p1 <- read.delim("../fromBroad/Plate1/counts-JD_GPP3297-Ramos_20220312_1.txt")
p2 <- read.delim("../fromBroad/Plate2/counts-JD_GPP3298-Ramos_20220312_2.txt")

p2.select <- p2 %>% dplyr::select(c(-Construct.IDs,-Unlabeled.Sample.Barcodes))

p1.p2 <- merge(p1,p2.select,by.x="Construct.Barcode",by.y="Construct.Barcode", all=TRUE)
```

## Import annotation

```{r}
CP1470.annot <- read.xlsx("CP1470.xlsx")
```

## Merge gene annotation with count table

```{r}
p1.p2.annot <- merge(CP1470.annot,p1.p2,by.x="Construct.Barcode",by.y="Construct.Barcode",all=TRUE)
p1.p2.annot <- p1.p2.annot %>% dplyr::select(c(-Construct.Barcode,-Category,-Construct.IDs.y))
p1.p2.annot <- p1.p2.annot %>% dplyr::rename(sgRNA=Construct.IDs.x,Gene=TargetGeneSymbol)
p1.p2.annot <- p1.p2.annot %>% arrange(sgRNA)
```

## original input file

```{r}
all.counts <- p1.p2.annot
```

# Importing normalized input data, l2 transform

```{r}
all.n <- read.table("batch.normalized.txt", row.names = 1, sep = "\t", header = TRUE)
```

## Log2 normalization with plus 1 offset

```{r}
all.n <- all.n %>% dplyr::select(-Gene)
all.n.l2 <- log((all.n+1),2)

colnames(all.n.l2)<-paste(colnames(all.n.l2),"l2",sep=".")
```

# Code used to make box and PCA plots from primary screen

## QC bolxplots

```{r,fig.width=12,fig.height=8}
validation.n.l2 <- all.n.l2 %>% rename_at(vars(everything()), ~str_replace_all(., ".l2", ""))
validation.n.l2.reorder <- validation.n.l2 %>% dplyr::select(starts_with("pDNA") | 
                                                          starts_with("Input") | 
                                                          starts_with("ah") | 
                                                          starts_with("am") | 
                                                          starts_with("NoCAR") |
                                                          starts_with("AR"))


tt <- validation.n.l2.reorder[,c(1:23,25,27,29,31,33,35,37,39,41,43,45,24,26,28,30,32,34,36,38,40,42,44,46)]
validation.n.l2.reorder <- tt
```

```{r,fig.width=8,fig.height=8}
validationBoxPlot <- ggplot(stack(validation.n.l2.reorder), aes(x = ind, y = values)) + geom_boxplot() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + ggtitle("all samples log2 normalized")

validationBoxPlot
```

## PCA Plots

```{r,fig.height=4,fig.width=5}
# Create an empty list to store the ggplot objects
PCAdata <- list()
PCAplots <- list()

# Read in sample annotations
AR.samps <- read_xlsx("AR_validation_conditions.xlsx")

# PCA of all samples together
plotTitle <- "All Validation Samples"
select.pca <- prcomp(t(validation.n.l2.reorder))
var <- select.pca$sdev^2
variance <- var/sum(var)
percentVar <- select.pca$sdev^2 / sum(select.pca$sdev^2 )
percentVar <- round(100 * percentVar,2)
select.pca$percentVar <- percentVar

select.pca$treatment <- AR.samps$treatment
select.pca$tissue <- AR.samps$tissue
select.pca$tissTreat <- paste0(AR.samps$tissue,".",AR.samps$treatment)

select.pca$samps <- colnames(validation.n.l2.reorder)

data <- as.data.frame(select.pca$x)
data$fill <- factor(select.pca$tissTreat)
plot <- ggplot(data, aes(x=PC1, y=PC2)) + geom_point(aes(fill = fill),shape=21, size = 4) + xlab(paste0("PC1 - ",select.pca$percentVar[1]," % of variability")) + ylab(paste0("PC2 - ",select.pca$percentVar[2]," % of variability")) + theme(legend.text = element_text(size = 8))

PCAdata[[plotTitle]] <- data
PCAplots[[plotTitle]] <- plot

# PCA of just in vitro

plotTitle <- "In vitro"
invitro.l2 <- validation.n.l2.reorder %>% dplyr::select(starts_with("pDNA") |
                                                          starts_with("Input") |
                                                          starts_with("ah") |
                                                          starts_with("am") |
                                                          starts_with("NoCAR"))
select.pca <- prcomp(t(invitro.l2))
var <- select.pca$sdev^2
variance <- var/sum(var)
percentVar <- select.pca$sdev^2 / sum(select.pca$sdev^2 )
percentVar <- round(100 * percentVar,2)
select.pca$percentVar <- percentVar

meta_df <- AR.samps %>% dplyr::filter(tissue == "inVitro") %>% dplyr::select(treatment)
select.pca$treatment <- meta_df$treatment
 
select.pca$samps <- colnames(invitro.l2)

data <- as.data.frame(select.pca$x)
data$fill <- factor(select.pca$treatment)
plot <- ggplot(data, aes(x=PC1, y=PC2)) + geom_point(aes(fill = fill),shape=21, size = 4) +
  xlab(paste0("PC1 - ",select.pca$percentVar[1]," % of variability")) +
  ylab(paste0("PC2 - ",select.pca$percentVar[2]," % of variability")) +
  theme(legend.text = element_text(size = 8)) + ggtitle(plotTitle)

PCAdata[[plotTitle]] <- data
PCAplots[[plotTitle]] <- plot

# PCA of BM

plotTitle <- "BM Samples"
invitro.l2 <- validation.n.l2.reorder %>% dplyr::select(ends_with("BM"))

select.pca <- prcomp(t(invitro.l2))
var <- select.pca$sdev^2
variance <- var/sum(var)
percentVar <- select.pca$sdev^2 / sum(select.pca$sdev^2 )
percentVar <- round(100 * percentVar,2)
select.pca$percentVar <- percentVar

meta_df <- AR.samps %>% dplyr::filter(tissue == "BM") %>% dplyr::select(treatment)
select.pca$treatment <- meta_df$treatment
 
select.pca$samps <- colnames(invitro.l2)

data <- as.data.frame(select.pca$x)
data$fill <- factor(select.pca$treatment)
plot <- ggplot(data, aes(x=PC1, y=PC2)) + geom_point(aes(fill = fill),shape=21, size = 4) +
  xlab(paste0("PC1 - ",select.pca$percentVar[1]," % of variability")) +
  ylab(paste0("PC2 - ",select.pca$percentVar[2]," % of variability")) +
  theme(legend.text = element_text(size = 8)) + ggtitle(plotTitle)

PCAdata[[plotTitle]] <- data
PCAplots[[plotTitle]] <- plot

# PCA of SP

plotTitle <- "SP Samples"
invitro.l2 <- validation.n.l2.reorder %>% dplyr::select(ends_with("SP"))

select.pca <- prcomp(t(invitro.l2))
var <- select.pca$sdev^2
variance <- var/sum(var)
percentVar <- select.pca$sdev^2 / sum(select.pca$sdev^2 )
percentVar <- round(100 * percentVar,2)
select.pca$percentVar <- percentVar

meta_df <- AR.samps %>% dplyr::filter(tissue == "SP") %>% dplyr::select(treatment)
select.pca$treatment <- meta_df$treatment
 
select.pca$samps <- colnames(invitro.l2)

data <- as.data.frame(select.pca$x)
data$fill <- factor(select.pca$treatment)
plot <- ggplot(data, aes(x=PC1, y=PC2)) + geom_point(aes(fill = fill),shape=21, size = 4) +
  xlab(paste0("PC1 - ",select.pca$percentVar[1]," % of variability")) +
  ylab(paste0("PC2 - ",select.pca$percentVar[2]," % of variability")) +
  theme(legend.text = element_text(size = 8)) + ggtitle(plotTitle)

PCAdata[[plotTitle]] <- data
PCAplots[[plotTitle]] <- plot
```

### Create plots

```{r,fig.width=18,fig.height=5}
#PCAplots[[1]]
pca.Together <- ggarrange(PCAplots[[2]],PCAplots[[3]],PCAplots[[4]], nrow=1,ncol=3)
pca.Together
```

### Build a QC figure

```{r,fig.width=12,fig.height=8}
ggarrange(validationBoxPlot,pca.Together,nrow=2,ncol=1)
```

## Write normalized data

```{r}
#all.counts <- read.xlsx("stockCounts.xlsx")
#all.counts <- all.counts %>% dplyr::select(-Gene)
#rownames(all.counts) <- all.counts[,1]
#all.counts <- all.counts %>% dplyr::select(-sgRNA)
#all.ct.l2 <- merge(x=all.counts,y=all.n.l2, by=0, all=TRUE, row.names=Row.names, Row.names=NULL)
#all.ct.l2 <- tibble::rownames_to_column(all.ct.l2, "sgRNA")
#write.xlsx(all.ct.l2, file="all.ct.l2.xlsx", overwrite = TRUE, rowNames=TRUE)
```

## additional sample stats
Count up numbers of guides with > 30 counts

```{r}
for(i in 1:ncol(all.counts)) {
  nn <- colnames(all.counts[i])
  n30 <- sum(all.counts[,i] > 30)
  print(paste(nn,n30))
}
```


## get some QC stats

```{r}
all.iqr <- as.data.frame(sapply(all.n.l2, IQR))
all.med <- as.data.frame(sapply(all.n.l2, median))
all.0 <- as.data.frame(colSums(all.n.l2 == 0))
all.stats <- cbind(all.0,all.med,all.iqr)

write.xlsx(all.stats, file="all.stats.xlsx", overwrite = TRUE, rowNames=TRUE)
```

# Mageck run on Linux cluster

see mageck_sr.sh

# Importing mageck test data and making plots

## SP_cd19.10m_v_egfr.15m

```{r,fig.height=8,fig.width=8}
SP_cd19.10m_v_egfr.15m.gdata <- ReadRRA("SP_cd19.10m_v_egfr.15m.gene_summary.txt", score = c("lfc", "rra")[1])
SP_cd19.10m_v_egfr.15m.sdata <- ReadsgRRA("SP_cd19.10m_v_egfr.15m.sgrna_summary.txt")

SP_cd19.10m_v_egfr.15m.gdata$negLogFDR = -log10(SP_cd19.10m_v_egfr.15m.gdata$FDR)
ScatterView(SP_cd19.10m_v_egfr.15m.gdata, x = "Score", y = "negLogFDR", 
            label = "id", model = "volcano", top = 15,
            display_cut = TRUE, max.overlaps = Inf)

SP_cd19.10m_v_egfr.15m.gdata$Rank = rank(SP_cd19.10m_v_egfr.15m.gdata$Score)
ScatterView(SP_cd19.10m_v_egfr.15m.gdata, x = "Rank", y = "Score", label = "id", 
                 top = 10, auto_cut_y = TRUE, ylab = "Log2FC", 
                 groups = c("top", "bottom"), max.overlaps = Inf) + 
  ggtitle("SP_cd19.10m_v_egfr.15m") + theme(plot.title = element_text(size = 12, face = "bold"))


ScatterView(SP_cd19.10m_v_egfr.15m.gdata, x = "Score", y = "Rank", label = "id", 
            auto_cut_x = TRUE, groups = c("left", "right"), 
            xlab = "Log2FC", top = 10, max.overlaps = Inf)
```

## SP_cd19.15m_v_egfr.15m

```{r,fig.height=8,fig.width=8}
SP_cd19.15m_v_egfr.15m.gdata <- ReadRRA("SP_cd19.15m_v_egfr.15m.gene_summary.txt", score = c("lfc", "rra")[1])
SP_cd19.15m_v_egfr.15m.sdata <- ReadsgRRA("SP_cd19.15m_v_egfr.15m.sgrna_summary.txt")

SP_cd19.15m_v_egfr.15m.gdata$negLogFDR = -log10(SP_cd19.15m_v_egfr.15m.gdata$FDR)
ScatterView(SP_cd19.15m_v_egfr.15m.gdata, x = "Score", y = "negLogFDR", 
            label = "id", model = "volcano", top = 15,
            display_cut = TRUE, max.overlaps = Inf)

SP_cd19.15m_v_egfr.15m.gdata$Rank = rank(SP_cd19.15m_v_egfr.15m.gdata$Score)
ScatterView(SP_cd19.15m_v_egfr.15m.gdata, x = "Rank", y = "Score", label = "id", 
                 top = 10, auto_cut_y = TRUE, ylab = "Log2FC", 
                 groups = c("top", "bottom"), max.overlaps = Inf) + 
  ggtitle("SP_cd19.15m_v_egfr.15m") + theme(plot.title = element_text(size = 12, face = "bold"))


ScatterView(SP_cd19.15m_v_egfr.15m.gdata, x = "Score", y = "Rank", label = "id", 
            auto_cut_x = TRUE, groups = c("left", "right"), 
            xlab = "Log2FC", top = 10, max.overlaps = Inf)
```

## BM_cd19.10m_v_egfr.15m

```{r,fig.height=8,fig.width=8}
BM_cd19.10m_v_egfr.15m.gdata <- ReadRRA("BM_cd19.10m_v_egfr.15m.gene_summary.txt", score = c("lfc", "rra")[1])
BM_cd19.10m_v_egfr.15m.sdata <- ReadsgRRA("BM_cd19.10m_v_egfr.15m.sgrna_summary.txt")

BM_cd19.10m_v_egfr.15m.gdata$negLogFDR = -log10(BM_cd19.10m_v_egfr.15m.gdata$FDR)
ScatterView(BM_cd19.10m_v_egfr.15m.gdata, x = "Score", y = "negLogFDR", 
            label = "id", model = "volcano", top = 15,
            display_cut = TRUE, max.overlaps = Inf)

BM_cd19.10m_v_egfr.15m.gdata$Rank = rank(BM_cd19.10m_v_egfr.15m.gdata$Score)
ScatterView(BM_cd19.10m_v_egfr.15m.gdata, x = "Rank", y = "Score", label = "id", 
                 top = 10, auto_cut_y = TRUE, ylab = "Log2FC", 
                 groups = c("top", "bottom"), max.overlaps = Inf) + 
  ggtitle("BM_cd19.10m_v_egfr.15m") + theme(plot.title = element_text(size = 12, face = "bold"))


ScatterView(BM_cd19.10m_v_egfr.15m.gdata, x = "Score", y = "Rank", label = "id", 
            auto_cut_x = TRUE, groups = c("left", "right"), 
            xlab = "Log2FC", top = 10, max.overlaps = Inf)
```

## BM_cd19.15m_v_egfr.15m

```{r,fig.height=8,fig.width=8}
BM_cd19.15m_v_egfr.15m.gdata <- ReadRRA("BM_cd19.15m_v_egfr.15m.gene_summary.txt", score = c("lfc", "rra")[1])
BM_cd19.15m_v_egfr.15m.sdata <- ReadsgRRA("BM_cd19.15m_v_egfr.15m.sgrna_summary.txt")

BM_cd19.15m_v_egfr.15m.gdata$negLogFDR = -log10(BM_cd19.15m_v_egfr.15m.gdata$FDR)
ScatterView(BM_cd19.15m_v_egfr.15m.gdata, x = "Score", y = "negLogFDR", 
            label = "id", model = "volcano", top = 15,
            display_cut = TRUE, max.overlaps = Inf)

BM_cd19.15m_v_egfr.15m.gdata$Rank = rank(BM_cd19.15m_v_egfr.15m.gdata$Score)
ScatterView(BM_cd19.15m_v_egfr.15m.gdata, x = "Rank", y = "Score", label = "id", 
                 top = 10, auto_cut_y = TRUE, ylab = "Log2FC", 
                 groups = c("top", "bottom"), max.overlaps = Inf) + 
  ggtitle("BM_cd19.15m_v_egfr.15m") + theme(plot.title = element_text(size = 12, face = "bold"))


ScatterView(BM_cd19.15m_v_egfr.15m.gdata, x = "Score", y = "Rank", label = "id", 
            auto_cut_x = TRUE, groups = c("left", "right"), 
            xlab = "Log2FC", top = 10, max.overlaps = Inf)
```

## cd19_1to2_v_egfr_1to2

```{r,fig.height=8,fig.width=8}
cd19_1to2_v_egfr_1to2.gdata <- ReadRRA("cd19_1to2_v_egfr_1to2.gene_summary.txt", score = c("lfc", "rra")[1])
cd19_1to2_v_egfr_1to2.sdata <- ReadsgRRA("cd19_1to2_v_egfr_1to2.sgrna_summary.txt")

cd19_1to2_v_egfr_1to2.gdata$negLogFDR = -log10(cd19_1to2_v_egfr_1to2.gdata$FDR)
ScatterView(cd19_1to2_v_egfr_1to2.gdata, x = "Score", y = "negLogFDR", 
            label = "id", model = "volcano", top = 15,
            display_cut = TRUE, max.overlaps = Inf)

cd19_1to2_v_egfr_1to2.gdata$Rank = rank(cd19_1to2_v_egfr_1to2.gdata$Score)
ScatterView(cd19_1to2_v_egfr_1to2.gdata, x = "Rank", y = "Score", label = "id", 
                 top = 10, auto_cut_y = TRUE, ylab = "Log2FC", 
                 groups = c("top", "bottom"), max.overlaps = Inf) + 
  ggtitle("cd19_1to2_v_egfr_1to2") + theme(plot.title = element_text(size = 12, face = "bold"))


ScatterView(cd19_1to2_v_egfr_1to2.gdata, x = "Score", y = "Rank", label = "id", 
            auto_cut_x = TRUE, groups = c("left", "right"), 
            xlab = "Log2FC", top = 10, max.overlaps = Inf)
```

## cd19_1to10_v_egfr_1to10

```{r,fig.height=8,fig.width=8}
cd19_1to10_v_egfr_1to10.gdata <- ReadRRA("cd19_1to10_v_egfr_1to10.gene_summary.txt", score = c("lfc", "rra")[1])
cd19_1to10_v_egfr_1to10.sdata <- ReadsgRRA("cd19_1to10_v_egfr_1to10.sgrna_summary.txt")

cd19_1to10_v_egfr_1to10.gdata$negLogFDR = -log10(cd19_1to10_v_egfr_1to10.gdata$FDR)
ScatterView(cd19_1to10_v_egfr_1to10.gdata, x = "Score", y = "negLogFDR", 
            label = "id", model = "volcano", top = 15,
            display_cut = TRUE, max.overlaps = Inf)

cd19_1to10_v_egfr_1to10.gdata$Rank = rank(cd19_1to10_v_egfr_1to10.gdata$Score)
ScatterView(cd19_1to10_v_egfr_1to10.gdata, x = "Rank", y = "Score", label = "id", 
                 top = 10, auto_cut_y = TRUE, ylab = "Log2FC",
                 groups = c("top", "bottom"), max.overlaps = Inf) + 
  ggtitle("cd19_1to10_v_egfr_1to10") + theme(plot.title = element_text(size = 12, face = "bold"))


ScatterView(cd19_1to10_v_egfr_1to10.gdata, x = "Score", y = "Rank", label = "id", 
            auto_cut_x = TRUE, groups = c("left", "right"), 
            xlab = "Log2FC", top = 10, max.overlaps = Inf)
```

# Assembling mageck gene-level fold change and FDR file

```{r}
SP.10m <- SP_cd19.10m_v_egfr.15m.gdata
colnames(SP.10m) <- c("id","SP.10m.Score","SP.10m.FDR","SP.10m.negLogFDR","SP.10m.Rank")
SP.15m <- SP_cd19.15m_v_egfr.15m.gdata
colnames(SP.15m) <- c("id","SP.15m.Score","SP.15m.FDR","SP.15m.negLogFDR","SP.15m.Rank")
BM.10m <- BM_cd19.10m_v_egfr.15m.gdata
colnames(BM.10m) <- c("id","BM.10m.Score","BM.10m.FDR","BM.10m.negLogFDR","BM.10m.Rank")
BM.15m <- BM_cd19.15m_v_egfr.15m.gdata
colnames(BM.15m) <- c("id","BM.15m.Score","BM.15m.FDR","BM.15m.negLogFDR","BM.15m.Rank")
ET.1.2 <- cd19_1to2_v_egfr_1to2.gdata
colnames(ET.1.2) <- c("id","ET.1.2.Score","ET.1.2.FDR","ET.1.2.negLogFDR","ET.1.2.Rank")
ET.1.10 <- cd19_1to10_v_egfr_1to10.gdata
colnames(ET.1.10) <- c("id","ET.1.10.Score","ET.1.10.FDR","ET.1.10.negLogFDR","ET.1.10.Rank")

Mageck.combined <- merge(x=SP.10m, y=SP.15m, by.x=c("id"),by.y=c("id"), all=TRUE)
Mageck.combined <- merge(x=Mageck.combined,y=BM.10m, by.x=c("id"),by.y=c("id"), all=TRUE)
Mageck.combined <- merge(x=Mageck.combined,y=BM.15m, by.x=c("id"),by.y=c("id"), all=TRUE)
Mageck.combined <- merge(x=Mageck.combined,y=ET.1.2, by.x=c("id"),by.y=c("id"), all=TRUE)
Mageck.combined <- merge(x=Mageck.combined,y=ET.1.10, by.x=c("id"),by.y=c("id"), all=TRUE)

write.xlsx(Mageck.combined, file="B-All_validationScreen_GeneLevel.xlsx")
```

# write session info

```{r}
sessionInfo()
writeLines(capture.output(sessionInfo()), "B-ALL_validationScreen_sessionInfo.txt")
```