---
title: "Keene - Data preparation and MAGEcK Flute"
author: "Charlie Whittaker"
date: "4/18/2022"
output: 
  html_document:
    toc: true
    toc_depth: 2
  html_notebook: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(tidy=FALSE, cache=TRUE,
                      dev="png", message=FALSE, error=FALSE, warning=TRUE)
```

# Load libraries

```{r, warning=FALSE,error=FALSE,message=FALSE}
library(openxlsx)
library(ggplot2)
library(tidyverse)
library(reprex)
library(matrixStats)
library(XML)
library(ggrepel)
library(DESeq2)
library(apeglm)
library(ComplexHeatmap)
library(dplyr)
library(readxl)
library(readr)
library(tximport)
library(edgeR)
library(MAGeCKFlute)
library(clusterProfiler)
library(extrafont)
loadfonts(device = "win")
```

# Count QC

```{r}
# countsummary <- read.delim("PrePost.countsummary.txt", check.names = FALSE)
# 
# BarView(countsummary, x = "Label", y = "GiniIndex",
#         ylab = "Gini index", main = "Evenness of sgRNA reads")
# 
# countsummary$Missed = log10(countsummary$Zerocounts)
# BarView(countsummary, x = "Label", y = "Missed", fill = "#394E80",
#         ylab = "Log10 missed gRNAs", main = "Missed sgRNAs")
# 
# MapRatesView(countsummary)
```

# Running full FluteRRA pipeline

```{r}
#file1 = file.path(system.file("extdata", package = "MAGeCKFlute"),
#                  "PostvPre.gene_summary.txt")
## path to the sgRNA summary file (optional)
#file2 = file.path(system.file("extdata", package = "MAGeCKFlute"),
#                  "PostvPre.sgrna_summary.txt")

#FluteRRA("PostvPre.gene_summary.txt",incorporateDepmap = FALSE, keytype = "Symbol", proj="PostVPre", organism="mmu", outdir = "./")
#FluteRRA("PostvPre.gene_summary.txt", "PostvPre.sgrna_summary.txt"", proj="PostVPre_plus_sgRNA", organism="mmu", outdir = "./")
```

# Import count tables including samples to be excluded

```{r}
p1p2.counts <- read.xlsx("klabbott_countsPlusGeneClean.xlsx")
```

# Importing normalized input data for KA experiments, l2 transform


```{r}
MPM_5_v_RPMI_5.n <- read.table("MPM_5_v_RPMI_5.normalized.txt", row.names = 1, sep = "\t", header = TRUE)
MPM_21_v_RPMI_21.n <- read.table("MPM_21_v_RPMI_21.normalized.txt", row.names = 1, sep = "\t", header = TRUE)
RPMI_5_v_RPMI_21.n <- read.table("RPMI_5_v_RPMI_21.normalized.txt", row.names = 1, sep = "\t", header = TRUE)
MPM_5_v_MPM_21 <- read.table("MPM_5_v_MPM_21.normalized.txt", row.names = 1, sep = "\t", header = TRUE)
```

## All 12 of KA samples are in the first 2 files

```{r}
MPM_5_v_RPMI_5.n <- MPM_5_v_RPMI_5.n %>% select(-Gene)
MPM_21_v_RPMI_21.n <- MPM_21_v_RPMI_21.n %>% select(-Gene)
RPMI_5_v_RPMI_21.n <- RPMI_5_v_RPMI_21.n %>% select(-Gene)
MPM_5_v_MPM_21 <- MPM_5_v_MPM_21 %>% select(-Gene)

KA.counts <- p1p2.counts %>% select(sgRNA,contains("KA"))

rownames(KA.counts) <- KA.counts[,1]
KA.counts <- KA.counts %>% select(-sgRNA)

KA.all <- transform(merge(x=MPM_5_v_RPMI_5.n,y=MPM_21_v_RPMI_21.n, by=0, all=TRUE), row.names=Row.names, Row.names=NULL)

KA.all.l2 <- log((KA.all+1),2)
colnames(KA.all.l2)<-paste(colnames(KA.all.l2),"l2",sep=".")
```

## Write normalized data

```{r}
KA.ct.l2 <- transform(merge(x=KA.counts,y=KA.all.l2, by=0, all=TRUE), row.names=Row.names, Row.names=NULL)
KA.ct.l2 <- tibble::rownames_to_column(KA.ct.l2, "sgRNA")
write.xlsx(KA.ct.l2, file="KA.ct.l2.xlsx", overwrite = TRUE, rowNames=TRUE)
```

# new QC bolxplots

```{r}
ggplot(stack(KA.all.l2), aes(x = ind, y = values)) + geom_boxplot() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + ggtitle("KA log2 normalized") 
```

## get some QC stats

```{r}
KA.iqr <- as.data.frame(sapply(KA.all.l2, IQR))
KA.med <- as.data.frame(sapply(KA.all.l2, median))
KA.0 <- as.data.frame(colSums(KA.all.l2 == 0))
KA.stats <- cbind(KA.0,KA.med,KA.iqr)

write.xlsx(KA.stats, file="KA.stats.xlsx", overwrite = TRUE, rowNames=TRUE)
```

## Calculate group averages

not applicable for this experiment

```{r}
# p12.Means <- p12.all.l2 %>% mutate(input.mean = select(., contains("input")) %>% rowMeans(na.rm = TRUE))
# p12.Means <- p12.Means %>% mutate(egfr.mean = select(., contains("egfr")) %>% rowMeans(na.rm = TRUE))
# p12.Means <- p12.Means %>% mutate(cd19.mean = select(., contains("cd19")) %>% rowMeans(na.rm = TRUE))
# p12.Means <- p12.Means %>% select(contains("mean"))
# write.xlsx(p12.Means, file="p12.Means.xlsx", overwrite = TRUE, rowNames=TRUE)
```

# Importing mageck test data and making plots

## MPM_21_v_RPMI_21

```{r,fig.height=4,fig.width=8}
MPM_21_v_RPMI_21.gdata <- ReadRRA("MPM_21_v_RPMI_21.gene_summary.txt", score = c("lfc", "rra")[1])
MPM_21_v_RPMI_21.sdata <- ReadsgRRA("MPM_21_v_RPMI_21.sgrna_summary.txt")

MPM_21_v_RPMI_21.gdata$negLogFDR = -log10(MPM_21_v_RPMI_21.gdata$FDR)
ScatterView(MPM_21_v_RPMI_21.gdata, x = "Score", y = "negLogFDR", 
            label = "id", model = "volcano", top = 8,
            display_cut = TRUE, max.overlaps = Inf)

MPM_21_v_RPMI_21.gdata$Rank = rank(MPM_21_v_RPMI_21.gdata$Score)
ScatterView(MPM_21_v_RPMI_21.gdata, x = "Rank", y = "Score", label = "id", 
                 top = 6, auto_cut_y = TRUE, ylab = "Log2FC", 
                 groups = c("top", "bottom"), max.overlaps = Inf)

ScatterView(MPM_21_v_RPMI_21.gdata, x = "Score", y = "Rank", label = "id", 
            auto_cut_x = TRUE, groups = c("left", "right"), 
            xlab = "Log2FC", top = 6, max.overlaps = Inf)
```

## MPM_5_v_RPMI_5

```{r,fig.height=4,fig.width=8}
MPM_5_v_RPMI_5.gdata <- ReadRRA("MPM_5_v_RPMI_5.gene_summary.txt", score = c("lfc", "rra")[1])
MPM_5_v_RPMI_5.sdata <- ReadsgRRA("MPM_5_v_RPMI_5.sgrna_summary.txt")

MPM_5_v_RPMI_5.gdata$negLogFDR = -log10(MPM_5_v_RPMI_5.gdata$FDR)
ScatterView(MPM_5_v_RPMI_5.gdata, x = "Score", y = "negLogFDR", 
            label = "id", model = "volcano", top = 8,
            display_cut = TRUE, max.overlaps = Inf)

MPM_5_v_RPMI_5.gdata$Rank = rank(MPM_5_v_RPMI_5.gdata$Score)
ScatterView(MPM_5_v_RPMI_5.gdata, x = "Rank", y = "Score", label = "id", 
                 top = 6, auto_cut_y = TRUE, ylab = "Log2FC", 
                 groups = c("top", "bottom"), max.overlaps = Inf)

ScatterView(MPM_5_v_RPMI_5.gdata, x = "Score", y = "Rank", label = "id", 
            auto_cut_x = TRUE, groups = c("left", "right"), 
            xlab = "Log2FC", top = 6, max.overlaps = Inf)
```

## RPMI_5_v_RPMI_21

```{r,fig.height=4,fig.width=8}
RPMI_5_v_RPMI_21.gdata <- ReadRRA("RPMI_5_v_RPMI_21.gene_summary.txt", score = c("lfc", "rra")[1])
RPMI_5_v_RPMI_21.sdata <- ReadsgRRA("RPMI_5_v_RPMI_21.sgrna_summary.txt")

RPMI_5_v_RPMI_21.gdata$negLogFDR = -log10(RPMI_5_v_RPMI_21.gdata$FDR)
ScatterView(RPMI_5_v_RPMI_21.gdata, x = "Score", y = "negLogFDR", 
            label = "id", model = "volcano", top = 8,
            display_cut = TRUE, max.overlaps = Inf)

RPMI_5_v_RPMI_21.gdata$Rank = rank(RPMI_5_v_RPMI_21.gdata$Score)
ScatterView(RPMI_5_v_RPMI_21.gdata, x = "Rank", y = "Score", label = "id", 
                 top = 6, auto_cut_y = TRUE, ylab = "Log2FC", 
                 groups = c("top", "bottom"), max.overlaps = Inf)

ScatterView(RPMI_5_v_RPMI_21.gdata, x = "Score", y = "Rank", label = "id", 
            auto_cut_x = TRUE, groups = c("left", "right"), 
            xlab = "Log2FC", top = 6, max.overlaps = Inf)
```

## MPM_5_v_MPM_21

```{r,fig.height=4,fig.width=8}
MPM_5_v_MPM_21.gdata <- ReadRRA("MPM_5_v_MPM_21.gene_summary.txt", score = c("lfc", "rra")[1])
MPM_5_v_MPM_21.sdata <- ReadsgRRA("MPM_5_v_MPM_21.sgrna_summary.txt")

MPM_5_v_MPM_21.gdata$negLogFDR = -log10(MPM_5_v_MPM_21.gdata$FDR)
ScatterView(MPM_5_v_MPM_21.gdata, x = "Score", y = "negLogFDR", 
            label = "id", model = "volcano", top = 8,
            display_cut = TRUE, max.overlaps = Inf)

MPM_5_v_MPM_21.gdata$Rank = rank(MPM_5_v_MPM_21.gdata$Score)
ScatterView(MPM_5_v_MPM_21.gdata, x = "Rank", y = "Score", label = "id", 
                 top = 6, auto_cut_y = TRUE, ylab = "Log2FC", 
                 groups = c("top", "bottom"), max.overlaps = Inf)

ScatterView(MPM_5_v_MPM_21.gdata, x = "Score", y = "Rank", label = "id", 
            auto_cut_x = TRUE, groups = c("left", "right"), 
            xlab = "Log2FC", top = 6, max.overlaps = Inf)
```

# Depmap test

Not relevant here, probably need to map to human symbols for this to work

```{r}
# depmap_similarity = ResembleDepmap(MPM_21_v_RPMI_21.gdata, symbol = "id", score = "Score")
```

# Viewing individual guides

## MPM_21_v_RPMI_21

```{r}
sgRankView(MPM_21_v_RPMI_21.sdata, top = 3, bottom = 3)

plotList <- MPM_21_v_RPMI_21.gdata %>% filter(abs(Score) > 1.2) %>% select(id)
sgRankView(MPM_21_v_RPMI_21.sdata, top = 0, bottom = 0, gene=plotList$id)
```

## MPM_5_v_RPMI_5

```{r}
sgRankView(MPM_5_v_RPMI_5.sdata, top = 3, bottom = 3)

plotList <- MPM_5_v_RPMI_5.gdata %>% filter(abs(Score) > 1.2) %>% select(id)
sgRankView(MPM_5_v_RPMI_5.sdata, top = 0, bottom = 0, gene=plotList$id)
```

## RPMI_5_v_RPMI_21

```{r}
sgRankView(RPMI_5_v_RPMI_21.sdata, top = 3, bottom = 3)

plotList <- RPMI_5_v_RPMI_21.gdata %>% filter(abs(Score) > 1.2) %>% select(id)
sgRankView(RPMI_5_v_RPMI_21.sdata, top = 0, bottom = 0, gene=plotList$id)
```

## MPM_5_v_MPM_21

```{r}
sgRankView(MPM_5_v_MPM_21.sdata, top = 3, bottom = 3)

plotList <- MPM_5_v_MPM_21.gdata %>% filter(abs(Score) > 1.2) %>% select(id)
sgRankView(MPM_5_v_MPM_21.sdata, top = 0, bottom = 0, gene=plotList$id)
```

# write session info

```{r}
sessionInfo()
writeLines(capture.output(sessionInfo()), "mageck_sessionInfo.txt")
```