---
title: "Data table preparation and MAGEcK Analysis for B-ALL"
author: "Charlie Whittaker"
date: "1/23/2023"
output: 
  html_document:
    toc: true
    toc_depth: 2
  html_notebook: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(tidy=FALSE, cache=TRUE,
                      dev="png", message=FALSE, error=FALSE, warning=TRUE)
```

# Load libraries

```{r, warning=FALSE,error=FALSE,message=FALSE}
library(openxlsx)
library(ggplot2)
library(tidyverse)
library(cowplot)
library(VennDiagram)
library(ggVennDiagram)
library(reprex)
library(matrixStats)
library(XML)
library(ggrepel)
library(ggpubr)
library(GGally)
library(DESeq2)
library(apeglm)
library(ComplexHeatmap)
library(dplyr)
library(readxl)
library(readr)
library(tximport)
library(edgeR)
library(MAGeCKFlute)
library(gprofiler2)
library(clusterProfiler)
library(fgsea)
```

# Import local code

```{r}
source('Rcode/data_formatting_tools.R')
source('Rcode/analysis_tools.R')
source('Rcode/plots.R')
source('Rcode/common.R')
source('Rcode/ssGSEAProjection.Library.R')
source('Rcode/gostplot_v2.R')
```

# Reading data

## Barcode Annotation file

This file is similar to sgRNAs but has some additional information

This can be adjusted in various ways. For example, when count of GeneSym is greater than 1, output will include results that are not official symbols.

```{r}
BarcodeAnnotations <- read_excel("BarcodeAnnotations.xlsx")
GeneSymWhitelist.selection <- BarcodeAnnotations %>% filter(NegativeControlGroup == 'No' & 
                                                    CountOfGeneSym <= 1 & 
                                                    GeneTargetInMultiplePools == 'No' &
                                                    between(BarcodesPerGene, 3,4))

GeneSymWhitelist <- unique(GeneSymWhitelist.selection %>% select(GeneSym,Pool)) %>% mutate(geneSym.whitelist = 'Yes')
#write.xlsx(GeneSymWhitelist,file='GeneSymWhitelist.xlsx')
```

## Read in sgRNA annotation file

This is used in the processing of the counts- files

```{r}
sgRNAs <- read.xlsx("../sgRNA_to_Gene_stock_plusPool.xlsx")
sgRNAs.gene <- sgRNAs %>% select(c("Barcode.Sequence","GeneSym","Pool"))
```

## Essential Genes

```{r}
hart <- read.xlsx("../Documents/hart_essential_MGI.xlsx")
essentialGenes <- read_xlsx("../Documents/essential_genes_combined_mouseSyms.xlsx")
```

## Mouse Gene to KEGG 

The human MsigDB Kegg GMT file was combined with MGI mouse to human orthogy data to build a table that associates mouse symbols with a yes/no
KEGG flag. This will allow us to highlight genes associated with some KEGG term in later plots.

```{r}
mmKEGG <- read_excel("../Documents/Mm_GeneSym_KEGG_association.xlsx")
mmKEGG.toJoin <- mmKEGG %>% select(MmSym,KEGG_Flag) %>% filter(KEGG_Flag == 'yes')
```

## Import IFNG sets

```{r}
biocarta.ifng <-read_excel("../Documents/BIOCARTA_IFNG_PATHWAY.xlsx")
hallmark.ifng <-read_excel("../Documents/HALLMARK_INTERFERON_GAMMA_RESPONSE.xlsx")
```

## Useful functions

```{r}
rowCount <- function(dat.table){
  as.data.frame(sapply(dat.table, length))
}

p1log2 <- function(dat.table){
  log2(dat.table+1)
}

summarizePool <- function(tt){
  tt <- merge(x=tt,y=sgRNAs.gene, by.x=c("Construct.Barcode"),by.y=c("Barcode.Sequence"), all=FALSE, all.x=TRUE)
  poolOut <-c()
  for (s in colnames(tt)){
    tmp <- tt %>% select(c("Construct.Barcode",s,"Pool"))
    tmp <- tmp %>% filter(!is.na(tmp[,s]))
    poolCt <- as.data.frame(table(tmp$Pool))
    poolOut <- rbind(poolOut,cbind(poolCt))
  }
  return(poolOut)
}

read_mageck_output <- function(outbase){
  print(outbase)
  assign(paste0(outbase,".gdata"),ReadRRA(paste0(outbase,".gene_summary.txt"), score = c("lfc", "rra")[1]))
  assign(paste0(outbase,".sdata"),ReadsgRRA(paste0(outbase,".sgrna_summary.txt")))
}

plot_gdata_volcano <- function(gdata){
  VolcanoView(gdata, x = "Score", y = "FDR", top = 10,
                 alpha=1, x_cutoff = log2(1.38), y_cutoff = 0.5,
                 mycolour = c("darkgrey", "#e41a1c", "#377eb8"),
                 ylab = "-Log10(FDR)", Label = "id") + ggtitle(i)
}

plot_essentials <- function(gdata.df){
  toPlot <- merge(x=gdata.df, y=hart, by.x="id" ,by.y="MGISym", all.x=TRUE)
  essential <- toPlot %>% filter(toPlot$hart_essential == "Y")
  degPlot <- ggplot() + 
    geom_point(data=toPlot, aes(x=Score, y=-log10(FDR)), col="grey") + 
    geom_point(data=essential, aes(x=Score, y=-log10(FDR)), col="red") + 
    theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(), 
                       panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))
  return(degPlot)
}

vlnplot_essentials <- function(df){
  Essential.toPlot <- merge(x=df, y=essentialGenes, by.x="id" ,by.y="MGISym", all.x=TRUE)
  Essential.toPlot <- merge(x=Essential.toPlot, y=GeneSymWhitelist, by.x="id" ,by.y="GeneSym", all.x=TRUE)
  Essential.toPlot <- Essential.toPlot %>% mutate(Essential = ifelse(is.na(Essential), "No", Essential))
  Essential.toPlot <- Essential.toPlot %>% dplyr::filter(geneSym.whitelist == "Yes")
  Essential.toPlot <- Essential.toPlot %>% rename(LFC = Score)
  data <- Essential.toPlot
  plot <- ggplot(data, aes(factor(Essential), LFC)) + geom_violin(fill='#A4A4A4') + geom_boxplot(width=.1) + ylim(-2.5, 2.5) +
    theme_bw() + 
    theme(plot.title = element_text(size = 8),axis.title.x = element_text(size = 8),axis.title.y = element_text(size = 8))
  return(plot)
}
```

## Importing Screen Count data from Broad files for Re-analysis

```{r}
dir1 = "../200406/filesTogether/"
#list.files(dir1,"counts")

dir2 = "../200627/filesTogether/"
#list.files(dir2,"counts")

dir3 = "../RH_resequenced_counts_files/"

files1 <- list.files(dir1,pattern="counts-*", full.names=TRUE)
files2 <- list.files(dir2,pattern="counts-*", full.names=TRUE)
files3 <- list.files(dir3,pattern="counts-*", full.names=TRUE)
```

```{r}
ldf.200406 <- lapply(files1, read.delim)
ldf.200627 <- lapply(files2, read.delim)
ldf.RH <- lapply(files3, read.delim)
```

## extract column names for the imported data and build dataframe that associated these values with a folder.object.file Index

```{r}
importedNames <- c()

for (i in 1:length(ldf.200406)){
  folder <- "200406"
  name <- colnames(ldf.200406[[i]])
  name <- as.data.frame(name)
  name <- tibble::rownames_to_column(name, "FileIndex")
  importedNames <- rbind(importedNames,cbind(Fold.Obj=paste0(folder,".",i),name))
}

for (i in 1:length(ldf.200627)){
  folder <- "200627"
  name <- colnames(ldf.200627[[i]])
  name <- as.data.frame(name)
  name <- tibble::rownames_to_column(name, "FileIndex")
  importedNames <- rbind(importedNames,cbind(Fold.Obj=paste0(folder,".",i),name))
}

for (i in 1:length(ldf.RH)){
  folder <- "RH"
  name <- colnames(ldf.RH[[i]])
  name <- as.data.frame(name)
  name <- tibble::rownames_to_column(name, "FileIndex")
  importedNames <- rbind(importedNames,cbind(Fold.Obj=paste0(folder,".",i),name))
}

importedNames <- importedNames %>% mutate(Folder.Obj.File_Index=paste0(Fold.Obj,".",FileIndex))
importedNames <- importedNames %>% select(name,Folder.Obj.File_Index)
```

## calculate medians, row counts and numbers of zeros

```{r}
List.Stats <- c()

for (i in 1:length(ldf.200406)){
  folder <- "200406"
  tmp.df <- mutate_if(ldf.200406[[i]], is.numeric, p1log2)
  List.Med <- as.data.frame(sapply(tmp.df, median))
  List.Med <- rename(List.Med, l2.median = `sapply(tmp.df, median)`)
  List.RowCount <- rowCount(ldf.200406[[i]])
  List.RowCount <- rename( List.RowCount, Row.Count = `sapply(dat.table, length)`)
  List.Zeros <- as.data.frame(colSums(ldf.200406[[i]]==0))
  List.Zeros <- rename(List.Zeros, ZeroCount = `colSums(ldf.200406[[i]] == 0)`)
  List.RowNumber <- as.data.frame(1:nrow(List.Med))
  List.RowNumber <- rename(List.RowNumber, FileIndex = `1:nrow(List.Med)`)
  List.Stats <- rbind(List.Stats,cbind(List.RowNumber,folder,i,List.Med,List.RowCount,List.Zeros))
}

for (i in 1:length(ldf.200627)){
  folder <- "200627"
  tmp.df <- mutate_if(ldf.200627[[i]], is.numeric, p1log2)
  List.Med <- as.data.frame(sapply(tmp.df, median))
  List.Med <- rename(List.Med, l2.median = `sapply(tmp.df, median)`)
  List.RowCount <- rowCount(ldf.200627[[i]])
  List.RowCount <- rename( List.RowCount, Row.Count = `sapply(dat.table, length)`)
  List.Zeros <- as.data.frame(colSums(ldf.200627[[i]]==0))
  List.Zeros <- rename(List.Zeros, ZeroCount = `colSums(ldf.200627[[i]] == 0)`)
  List.RowNumber <- as.data.frame(1:nrow(List.Med))
  List.RowNumber <- rename(List.RowNumber, FileIndex = `1:nrow(List.Med)`)
  List.Stats <- rbind(List.Stats,cbind(List.RowNumber,folder,i,List.Med,List.RowCount,List.Zeros))
}

for (i in 1:length(ldf.RH)){
  folder <- "RH"
  tmp.df <- mutate_if(ldf.RH[[i]], is.numeric, p1log2)
  List.Med <- as.data.frame(sapply(tmp.df, median))
  List.Med <- rename(List.Med, l2.median = `sapply(tmp.df, median)`)
  List.RowCount <- rowCount(ldf.RH[[i]])
  List.RowCount <- rename( List.RowCount, Row.Count = `sapply(dat.table, length)`)
  List.Zeros <- as.data.frame(colSums(ldf.RH[[i]]==0))
  List.Zeros <- rename(List.Zeros, ZeroCount = `colSums(ldf.RH[[i]] == 0)`)
  List.RowNumber <- as.data.frame(1:nrow(List.Med))
  List.RowNumber <- rename(List.RowNumber, FileIndex = `1:nrow(List.Med)`)
  List.Stats <- rbind(List.Stats,cbind(List.RowNumber,folder,i,List.Med,List.RowCount,List.Zeros))
}

List.Stats <- rename(List.Stats, ObjIndex = `i`)
List.Stats <- List.Stats %>% mutate(Folder.Obj.File_Index=paste0(folder,".",ObjIndex,".",FileIndex))
List.Stats <- List.Stats %>% select(Folder.Obj.File_Index,l2.median,Row.Count,ZeroCount)
```

## Summarize Pool per sample

```{r}
poolSummary <- c()

for (i in 1:length(ldf.200406)){
  folder <- "200406"
  poolCt <- summarizePool(ldf.200406[[i]])
  poolCt <- tibble::rownames_to_column(poolCt, "FileIndex")
  poolSummary <- rbind(poolSummary,cbind(Fold.Obj=paste0(folder,".",i),poolCt))
}

for (i in 1:length(ldf.200627)){
  folder <- "200627"
  poolCt <- summarizePool(ldf.200627[[i]])
  poolCt <- tibble::rownames_to_column(poolCt, "FileIndex")
  poolSummary <- rbind(poolSummary,cbind(Fold.Obj=paste0(folder,".",i),poolCt))
}

for (i in 1:length(ldf.RH)){
  folder <- "RH"
  poolCt <- summarizePool(ldf.RH[[i]])
  poolCt <- tibble::rownames_to_column(poolCt, "FileIndex")
  poolSummary <- rbind(poolSummary,cbind(Fold.Obj=paste0(folder,".",i),poolCt))
}

poolSummary <- rename(poolSummary, DetectedPool = Var1)
poolSummary <- poolSummary %>% mutate(Folder.Obj.File_Index=paste0(Fold.Obj,".",FileIndex))
poolSummary <- poolSummary %>% select(Folder.Obj.File_Index,DetectedPool,Freq)
```

```{r}
qcObject <- merge(x=importedNames,y=List.Stats, by.x='Folder.Obj.File_Index',by.y='Folder.Obj.File_Index', all=TRUE)
qcObject <- merge(x=qcObject,y=poolSummary, by.x='Folder.Obj.File_Index',by.y='Folder.Obj.File_Index', all=FALSE,all.x=TRUE)
write.xlsx(qcObject,file="qcObject_plusRH.xlsx")
```

# Building dataframes for mageck testing, running tests and importing results

There are numerous pools and conditions to compare and columns containing the data are scattered in the 91 input files.
These commands extract, assembly and re-order each set of columns. Data are then exported for mageck testing and results are imported.

# In vitro

## In Vitro Pool A

identify columns with non-0 medians

```{r}
invitro.poolA.1 <- ldf.200406[[1]][c(1,6,15,16,17,18,19,20)]
invitro.poolA.2 <- ldf.200406[[7]][c(1,8,9,10,11,12,13,26)]
invitro.poolA.3 <- ldf.200627[[61]][c(1,3)]

invitro.poolA <- merge(x=invitro.poolA.1,y=invitro.poolA.2, by.x=c("Construct.Barcode"),by.y=c("Construct.Barcode"), all=TRUE)
invitro.poolA <- merge(x=invitro.poolA,y=invitro.poolA.3, by.x=c("Construct.Barcode"),by.y=c("Construct.Barcode"), all=TRUE)
invitro.poolA <- merge(x=invitro.poolA,y=sgRNAs.gene, by.x=c("Construct.Barcode"),by.y=c("Barcode.Sequence"), all=FALSE, all.x=TRUE)

col.vit.poolA <- colnames(invitro.poolA)
```

```{r}
# reorder columns
invitro.poolA.reorder <- invitro.poolA[,c(1,17,2,15,
                                          3,4,5,16,
                                          6,7,8,
                                          9,10,11,
                                          12,13,14)]
# replace NA values with 0
invitro.poolA.reorder <- replace(invitro.poolA.reorder, is.na(invitro.poolA.reorder), 0)
# Write to table for mageck run
write_delim(invitro.poolA.reorder,file="invitro.poolA.txt", delim = '\t')
```

### results import and plotting

```{r}
files.toPlot <- list.files(pattern=glob2rx("invitro.poolA_*gene_summary.txt"), full.names=FALSE)
files.toPlot <- str_replace(files.toPlot, ".gene_summary.txt", "")
files.toPlot

for (i in files.toPlot){
  assign(paste0(i,".gdata"),ReadRRA(paste0(i,".gene_summary.txt"), score = c("lfc", "rra")[1]))
  assign(paste0(i,".sdata"),ReadsgRRA(paste0(i,".sgrna_summary.txt")))
}  

for (i in files.toPlot){
  x <- get(paste0(i,".gdata"))
  print(plot_gdata_volcano(x))
}
```

## In Vitro Pool B

identify columns with non-0 medians

```{r}
invitro.poolB.1 <- ldf.200406[[4]][c(1,7,21,22,23,25,26)]
invitro.poolB.2 <- ldf.200406[[9]][c(1,14,15,16,17,18,27)]
invitro.poolB.3 <- ldf.200627[[63]][c(1,4,5)]

invitro.poolB <- merge(x=invitro.poolB.1,y=invitro.poolB.2, by.x=c("Construct.Barcode"),by.y=c("Construct.Barcode"), all=TRUE)
invitro.poolB <- merge(x=invitro.poolB,y=invitro.poolB.3, by.x=c("Construct.Barcode"),by.y=c("Construct.Barcode"), all=TRUE)
#invitro.poolB <- merge(x=invitro.poolB,y=invitro.poolB.4, by.x=c("Construct.Barcode"),by.y=c("Construct.Barcode"), all=TRUE)
invitro.poolB <- merge(x=invitro.poolB,y=sgRNAs.gene, by.x=c("Construct.Barcode"),by.y=c("Barcode.Sequence"), all=FALSE, all.x=TRUE)

col.vit.poolB <- colnames(invitro.poolB)
```

```{r}
# reorder columns

invitro.poolB.reorder <- invitro.poolB[,c(1,16,2,
                                          13,
                                          3,4,5,
                                          6,7,14,
                                          8,9,10,15,
                                          11,12)]

# replace NA values with 0
invitro.poolB.reorder <- replace(invitro.poolB.reorder, is.na(invitro.poolB.reorder), 0)

# Write to table for mageck run
write_delim(invitro.poolB.reorder,file="invitro.poolB.txt", delim = '\t')
```

### results import and plotting

```{r}
files.toPlot <- list.files(pattern=glob2rx("invitro.poolB_*gene_summary.txt"), full.names=FALSE)
files.toPlot <- str_replace(files.toPlot, ".gene_summary.txt", "")
files.toPlot

for (i in files.toPlot){
  assign(paste0(i,".gdata"),ReadRRA(paste0(i,".gene_summary.txt"), score = c("lfc", "rra")[1]))
  assign(paste0(i,".sdata"),ReadsgRRA(paste0(i,".sgrna_summary.txt")))
}  

for (i in files.toPlot){
  x <- get(paste0(i,".gdata"))
  print(plot_gdata_volcano(x))
}
```

## In Vitro Pool C

```{r}
invitro.poolC.1 <- ldf.200406[[2]][c(1,8,27)]
invitro.poolC.2 <- ldf.200406[[8]][c(1,3,4,5,6,7,20,21,22,23,24,25)]
invitro.poolC.3 <- ldf.200406[[10]][c(1,3)]

invitro.poolC <- merge(x=invitro.poolC.1,y=invitro.poolC.2, by.x=c("Construct.Barcode"),by.y=c("Construct.Barcode"), all=TRUE)
invitro.poolC <- merge(x=invitro.poolC,y=invitro.poolC.3, by.x=c("Construct.Barcode"),by.y=c("Construct.Barcode"), all=TRUE)
invitro.poolC <- merge(x=invitro.poolC,y=sgRNAs.gene, by.x=c("Construct.Barcode"),by.y=c("Barcode.Sequence"), all=FALSE, all.x=TRUE)

col.vit.poolC <- colnames(invitro.poolC)
```

```{r}
# reorder columns
invitro.poolC.reorder <- invitro.poolC[,c(1,16,2,15,
                                  3,4,5,
                                  6,7,8,
                                  9,10,11,
                                  12,13,14)]

# replace NA values with 0
invitro.poolC.reorder <- replace(invitro.poolC.reorder, is.na(invitro.poolC.reorder), 0)

# Write to table for mageck run
write_delim(invitro.poolC.reorder,file="invitro.poolC.txt", delim = '\t')
```

### results import and plotting

```{r}
files.toPlot <- list.files(pattern=glob2rx("invitro.poolC_*gene_summary.txt"), full.names=FALSE)
files.toPlot <- str_replace(files.toPlot, ".gene_summary.txt", "")
files.toPlot

for (i in files.toPlot){
  assign(paste0(i,".gdata"),ReadRRA(paste0(i,".gene_summary.txt"), score = c("lfc", "rra")[1]))
  assign(paste0(i,".sdata"),ReadsgRRA(paste0(i,".sgrna_summary.txt")))
}  

for (i in files.toPlot){
  x <- get(paste0(i,".gdata"))
  print(plot_gdata_volcano(x))
}
```

## In Vitro Pool D

```{r}
invitro.poolD.1 <- ldf.200406[[3]][c(1,12)]
invitro.poolD.2 <- ldf.200406[[11]][c(1,4,5,6,7,8,9,18,19,20,21,22,23)]
invitro.poolD.3 <- ldf.200406[[15]][c(1,14)]

invitro.poolD <- merge(x=invitro.poolD.1,y=invitro.poolD.2, by.x=c("Construct.Barcode"),by.y=c("Construct.Barcode"), all=TRUE)
invitro.poolD <- merge(x=invitro.poolD,y=invitro.poolD.3, by.x=c("Construct.Barcode"),by.y=c("Construct.Barcode"), all=TRUE)
invitro.poolD <- merge(x=invitro.poolD,y=sgRNAs.gene, by.x=c("Construct.Barcode"),by.y=c("Barcode.Sequence"), all=FALSE, all.x=TRUE)

col.vit.poolD <- colnames(invitro.poolD)
```

```{r}
# reorder columns
invitro.poolD.reorder <- invitro.poolD[,c(1,16,2,15,
                                  3,4,5,
                                  6,7,8,
                                  9,10,11,
                                  12,13,14)]

# replace NA values with 0
invitro.poolD.reorder <- replace(invitro.poolD.reorder, is.na(invitro.poolD.reorder), 0)

# Write to table for mageck run
write_delim(invitro.poolD.reorder,file="invitro.poolD.txt", delim = '\t')
```

### results import and plotting

```{r}
files.toPlot <- list.files(pattern=glob2rx("invitro.poolD_*gene_summary.txt"), full.names=FALSE)
files.toPlot <- str_replace(files.toPlot, ".gene_summary.txt", "")
files.toPlot

for (i in files.toPlot){
  assign(paste0(i,".gdata"),ReadRRA(paste0(i,".gene_summary.txt"), score = c("lfc", "rra")[1]))
  assign(paste0(i,".sdata"),ReadsgRRA(paste0(i,".sgrna_summary.txt")))
}  

for (i in files.toPlot){
  x <- get(paste0(i,".gdata"))
  print(plot_gdata_volcano(x))
}
```

## In Vitro Pool E

```{r}
invitro.poolE.1 <- ldf.200406[[5]][c(1,13)]
invitro.poolE.2 <- ldf.200406[[12]][c(1,10,11,12,13,14,24)]
invitro.poolE.3 <- ldf.200406[[16]][c(1,3,4,5,6,7,15)]

invitro.poolE <- merge(x=invitro.poolE.1,y=invitro.poolE.2, by.x=c("Construct.Barcode"),by.y=c("Construct.Barcode"), all=TRUE)
invitro.poolE <- merge(x=invitro.poolE,y=invitro.poolE.3, by.x=c("Construct.Barcode"),by.y=c("Construct.Barcode"), all=TRUE)
invitro.poolE <- merge(x=invitro.poolE,y=sgRNAs.gene, by.x=c("Construct.Barcode"),by.y=c("Barcode.Sequence"), all=FALSE, all.x=TRUE)

col.vit.poolE <- colnames(invitro.poolE)
```

```{r}
# reorder columns
invitro.poolE.reorder <- invitro.poolE[,c(1,15,2,14,
                                  3,4,
                                  5,6,7,
                                  8,9,10,
                                  11,12,13)]

# replace NA values with 0
invitro.poolE.reorder <- replace(invitro.poolE.reorder, is.na(invitro.poolE.reorder), 0)

# Write to table for mageck run
write_delim(invitro.poolE.reorder,file="invitro.poolE.txt", delim = '\t')
```

### results import and plotting

```{r}
files.toPlot <- list.files(pattern=glob2rx("invitro.poolE_*gene_summary.txt"), full.names=FALSE)
files.toPlot <- str_replace(files.toPlot, ".gene_summary.txt", "")
files.toPlot

for (i in files.toPlot){
  assign(paste0(i,".gdata"),ReadRRA(paste0(i,".gene_summary.txt"), score = c("lfc", "rra")[1]))
  assign(paste0(i,".sdata"),ReadsgRRA(paste0(i,".sgrna_summary.txt")))
}  

for (i in files.toPlot){
  x <- get(paste0(i,".gdata"))
  print(plot_gdata_volcano(x))
}
```

## In Vitro Pool F

```{r}
invitro.poolF.1 <- ldf.200406[[6]][c(1,14)]
invitro.poolF.2 <- ldf.200406[[13]][c(1,15,16,17)]
invitro.poolF.3 <- ldf.200406[[17]][c(1,8,9,10,11,16)]
invitro.poolF.4 <- ldf.200627[[64]][c(1,7,8)]
invitro.poolF.5 <- ldf.RH[[3]][c(1,3,4,5)]

invitro.poolF <- merge(x=invitro.poolF.1,y=invitro.poolF.2, by.x=c("Construct.Barcode"),by.y=c("Construct.Barcode"), all=TRUE)
invitro.poolF <- merge(x=invitro.poolF,y=invitro.poolF.3, by.x=c("Construct.Barcode"),by.y=c("Construct.Barcode"), all=TRUE)
invitro.poolF <- merge(x=invitro.poolF,y=invitro.poolF.4, by.x=c("Construct.Barcode"),by.y=c("Construct.Barcode"), all=TRUE)
invitro.poolF <- merge(x=invitro.poolF,y=invitro.poolF.5, by.x=c("Construct.Barcode"),by.y=c("Construct.Barcode"), all=TRUE)
invitro.poolF <- merge(x=invitro.poolF,y=sgRNAs.gene, by.x=c("Construct.Barcode"),by.y=c("Barcode.Sequence"), all=FALSE, all.x=TRUE)

col.vit.poolF <- colnames(invitro.poolF)
```

```{r}
# reorder columns
invitro.poolF.reorder <- invitro.poolF[,c(1,16,2,10,
                                  3,4,5,
                                  13,14,15,
                                  6,7,8,
                                  9,11,12)]

# replace NA values with 0
invitro.poolF.reorder <- replace(invitro.poolF.reorder, is.na(invitro.poolF.reorder), 0)
# Write to table for mageck run
write_delim(invitro.poolF.reorder,file="invitro.poolF.txt", delim = '\t')
```

### results import and plotting

```{r}
files.toPlot <- list.files(pattern=glob2rx("invitro.poolF_*gene_summary.txt"), full.names=FALSE)
files.toPlot <- str_replace(files.toPlot, ".gene_summary.txt", "")
files.toPlot

for (i in files.toPlot){
  assign(paste0(i,".gdata"),ReadRRA(paste0(i,".gene_summary.txt"), score = c("lfc", "rra")[1]))
  assign(paste0(i,".sdata"),ReadsgRRA(paste0(i,".sgrna_summary.txt")))
}  

for (i in files.toPlot){
  x <- get(paste0(i,".gdata"))
  print(plot_gdata_volcano(x))
}
```

# In Vivo

## In Vivo Pool A

```{r}
invivo.poolA.1 <- ldf.200406[[1]][c(1,3)]
invivo.poolA.2 <- ldf.200406[[14]][c(1,23,24)]
invivo.poolA.3 <- ldf.200406[[18]][c(1,3,4)]
invivo.poolA.4 <- ldf.200627[[61]][c(1,9,10,11,13,23,24,25,26,27,28,29)]
invivo.poolA.RH <- ldf.RH[[1]][c(1,6,7,8,9,10,11)]

invivo.poolA <- merge(x=invivo.poolA.1,y=invivo.poolA.2, by.x=c("Construct.Barcode"),by.y=c("Construct.Barcode"), all=TRUE)
invivo.poolA <- merge(x=invivo.poolA,y=invivo.poolA.3, by.x=c("Construct.Barcode"),by.y=c("Construct.Barcode"), all=TRUE)
invivo.poolA <- merge(x=invivo.poolA,y=invivo.poolA.4, by.x=c("Construct.Barcode"),by.y=c("Construct.Barcode"), all=TRUE)
invivo.poolA <- merge(x=invivo.poolA,y=invivo.poolA.RH, by.x=c("Construct.Barcode"),by.y=c("Construct.Barcode"), all=TRUE)
invivo.poolA <- merge(x=invivo.poolA,y=sgRNAs.gene, by.x=c("Construct.Barcode"),by.y=c("Barcode.Sequence"), all=FALSE, all.x=TRUE)

col.viv.poolA <- colnames(invivo.poolA)
```

```{r}
# reorder columns
invivo.poolA.reorder <- invivo.poolA[,c(1,24,2,
                                3,5,18,20,22,
                                11,13,16,
                                7,8,9,10,
                                4,6,19,21,23,
                                12,14,15,17)]

# replace NA values with 0
invivo.poolA.reorder <- replace(invivo.poolA.reorder, is.na(invivo.poolA.reorder), 0)
# Write to table for mageck run
write_delim(invivo.poolA.reorder,file="invivo.poolA.txt", delim = '\t')
```

### results import and plotting

```{r}
files.toPlot <- list.files(pattern=glob2rx("invivo.poolA_*gene_summary.txt"), full.names=FALSE)
files.toPlot <- str_replace(files.toPlot, ".gene_summary.txt", "")
files.toPlot

for (i in files.toPlot){
  assign(paste0(i,".gdata"),ReadRRA(paste0(i,".gene_summary.txt"), score = c("lfc", "rra")[1]))
  assign(paste0(i,".sdata"),ReadsgRRA(paste0(i,".sgrna_summary.txt")))
}

for (i in files.toPlot){
  x <- get(paste0(i,".gdata"))
  print(plot_gdata_volcano(x))
}
```

## In Vivo Pool B

```{r}
invivo.poolB.1 <- ldf.200406[[4]][c(1,4)]
invivo.poolB.2 <- ldf.200406[[20]][c(1,5,6,7,8,9,10,11,12,14,15,16)]
invivo.poolB.3 <- ldf.200627[[58]][c(1,3,4,5,6,7,8)]
invivo.poolB.4 <- ldf.200627[[63]][c(1,14,15,16,17,30,31)]


invivo.poolB <- merge(x=invivo.poolB.1,y=invivo.poolB.2, by.x=c("Construct.Barcode"),by.y=c("Construct.Barcode"), all=TRUE)
invivo.poolB <- merge(x=invivo.poolB,y=invivo.poolB.3, by.x=c("Construct.Barcode"),by.y=c("Construct.Barcode"), all=TRUE)
invivo.poolB <- merge(x=invivo.poolB,y=invivo.poolB.4, by.x=c("Construct.Barcode"),by.y=c("Construct.Barcode"), all=TRUE)
invivo.poolB <- merge(x=invivo.poolB,y=sgRNAs.gene, by.x=c("Construct.Barcode"),by.y=c("Barcode.Sequence"), all=FALSE, all.x=TRUE)

col.viv.poolB <- colnames(invivo.poolB)
```

```{r}
# reorder columns
invivo.poolB.reorder <- invivo.poolB[,c(1,26,2,
                                3,5,7,9,12,
                                15,17,25,
                                20,21,22,23,
                                4,6,8,10,11,13,
                                14,16,18,19,24)]

# replace NA values with 0
invivo.poolB.reorder <- replace(invivo.poolB.reorder, is.na(invivo.poolB.reorder), 0)
# Write to table for mageck run
write_delim(invivo.poolB.reorder,file="invivo.poolB.txt", delim = '\t')
```

### results import and plotting

```{r}
files.toPlot <- list.files(pattern=glob2rx("invivo.poolB_*gene_summary.txt"), full.names=FALSE)
files.toPlot <- str_replace(files.toPlot, ".gene_summary.txt", "")
files.toPlot

for (i in files.toPlot){
  assign(paste0(i,".gdata"),ReadRRA(paste0(i,".gene_summary.txt"), score = c("lfc", "rra")[1]))
  assign(paste0(i,".sdata"),ReadsgRRA(paste0(i,".sgrna_summary.txt")))
}

for (i in files.toPlot){
  x <- get(paste0(i,".gdata"))
  print(plot_gdata_volcano(x))
}
```

## In Vivo Pool C

```{r}
invivo.poolC.1 <- ldf.200406[[2]][c(1,5)]
invivo.poolC.2 <- ldf.200406[[19]][c(1,17,18,19,20,21,22,23,24,26)]
invivo.poolC.3 <- ldf.200627[[56]][c(1,9,10,11,12,13,14,15,16,17)]
invivo.poolC.4 <- ldf.200627[[62]][c(1,18,19,20,21,22)]

invivo.poolC <- merge(x=invivo.poolC.1,y=invivo.poolC.2, by.x=c("Construct.Barcode"),by.y=c("Construct.Barcode"), all=TRUE)
invivo.poolC <- merge(x=invivo.poolC,y=invivo.poolC.3, by.x=c("Construct.Barcode"),by.y=c("Construct.Barcode"), all=TRUE)
invivo.poolC <- merge(x=invivo.poolC,y=invivo.poolC.4, by.x=c("Construct.Barcode"),by.y=c("Construct.Barcode"), all=TRUE)
invivo.poolC <- merge(x=invivo.poolC,y=sgRNAs.gene, by.x=c("Construct.Barcode"),by.y=c("Barcode.Sequence"), all=FALSE, all.x=TRUE)

col.viv.poolC <- colnames(invivo.poolC)
```

```{r}
# reorder columns

invivo.poolC.reorder <- invivo.poolC[,c(1,26,2,
                                3,5,7,9,
                                13,15,18,20,
                                21,22,23,24,25,
                                4,6,8,10,11,
                                12,14,16,17,19)]

# replace NA values with 0
invivo.poolC.reorder <- replace(invivo.poolC.reorder, is.na(invivo.poolC.reorder), 0)
# Write to table for mageck run
write_delim(invivo.poolC.reorder,file="invivo.poolC.txt", delim = '\t')
```

### results import and plotting

```{r}
files.toPlot <- list.files(pattern=glob2rx("invivo.poolC_*gene_summary.txt"), full.names=FALSE)
files.toPlot <- str_replace(files.toPlot, ".gene_summary.txt", "")
files.toPlot

for (i in files.toPlot){
  assign(paste0(i,".gdata"),ReadRRA(paste0(i,".gene_summary.txt"), score = c("lfc", "rra")[1]))
  assign(paste0(i,".sdata"),ReadsgRRA(paste0(i,".sgrna_summary.txt")))
}

for (i in files.toPlot){
  x <- get(paste0(i,".gdata"))
  print(plot_gdata_volcano(x))
}
```

## In Vivo Pool D

```{r}
invivo.poolD.1 <- ldf.200406[[3]][c(1,9)]
invivo.poolD.2 <- ldf.200627[[51]][c(1,14,15,16,17,18,19,30,31,32,33,34,35,36,37,38)]
invivo.poolD.3 <- ldf.200627[[57]][c(1,18,19,20,21,22,23,24,25,26,27)]

invivo.poolD <- merge(x=invivo.poolD.1,y=invivo.poolD.2, by.x=c("Construct.Barcode"),by.y=c("Construct.Barcode"), all=TRUE)
invivo.poolD <- merge(x=invivo.poolD,y=invivo.poolD.3, by.x=c("Construct.Barcode"),by.y=c("Construct.Barcode"), all=TRUE)
invivo.poolD <- merge(x=invivo.poolD,y=sgRNAs.gene, by.x=c("Construct.Barcode"),by.y=c("Barcode.Sequence"), all=FALSE, all.x=TRUE)

col.viv.poolD <- colnames(invivo.poolD)
```

```{r}
# reorder columns
invivo.poolD.reorder <- invivo.poolD[,c(1,28,2,
                                18,20,22,24,26,
                                9,11,13,15,
                                3,4,5,6,7,8,
                                19,21,23,25,27,
                                10,12,14,16,17)]

# replace NA values with 0
invivo.poolD.reorder <- replace(invivo.poolD.reorder, is.na(invivo.poolD.reorder), 0)
# Write to table for mageck run
write_delim(invivo.poolD.reorder,file="invivo.poolD.txt", delim = '\t')
```

### results import and plotting

```{r}
files.toPlot <- list.files(pattern=glob2rx("invivo.poolD_*gene_summary.txt"), full.names=FALSE)
files.toPlot <- str_replace(files.toPlot, ".gene_summary.txt", "")
files.toPlot

for (i in files.toPlot){
  assign(paste0(i,".gdata"),ReadRRA(paste0(i,".gene_summary.txt"), score = c("lfc", "rra")[1]))
  assign(paste0(i,".sdata"),ReadsgRRA(paste0(i,".sgrna_summary.txt")))
}

for (i in files.toPlot){
  x <- get(paste0(i,".gdata"))
  print(plot_gdata_volcano(x))
}
```

## In Vivo Pool E

```{r}
invivo.poolE.1 <- ldf.200406[[5]][c(1,10)]
invivo.poolE.2 <- ldf.200627[[52]][c(1,3,20,21,22,23,24,39,40,41,42,43,44,45,46,47,48)]
invivo.poolE.3 <- ldf.200627[[59]][c(1,28,29,30,31,32,33,34,35,36,37,38)]

invivo.poolE <- merge(x=invivo.poolE.1,y=invivo.poolE.2, by.x=c("Construct.Barcode"),by.y=c("Construct.Barcode"), all=TRUE)
invivo.poolE <- merge(x=invivo.poolE,y=invivo.poolE.3, by.x=c("Construct.Barcode"),by.y=c("Construct.Barcode"), all=TRUE)
invivo.poolE <- merge(x=invivo.poolE,y=sgRNAs.gene, by.x=c("Construct.Barcode"),by.y=c("Barcode.Sequence"), all=FALSE, all.x=TRUE)

col.viv.poolE <- colnames(invivo.poolE)
```

```{r}
# reorder columns
invivo.poolE.reorder <- invivo.poolE[,c(1,30,2,
                                19,21,23,25,27,29,
                                9,11,14,16,18,
                                4,5,6,7,8,
                                3,20,22,24,26,28,
                                10,12,13,15,17)]

# replace NA values with 0
invivo.poolE.reorder <- replace(invivo.poolE.reorder, is.na(invivo.poolE.reorder), 0)
# Write to table for mageck run
write_delim(invivo.poolE.reorder,file="invivo.poolE.txt", delim = '\t')
```

### results import and plotting

```{r}
files.toPlot <- list.files(pattern=glob2rx("invivo.poolE_*gene_summary.txt"), full.names=FALSE)
files.toPlot <- str_replace(files.toPlot, ".gene_summary.txt", "")
files.toPlot

for (i in files.toPlot){
  assign(paste0(i,".gdata"),ReadRRA(paste0(i,".gene_summary.txt"), score = c("lfc", "rra")[1]))
  assign(paste0(i,".sdata"),ReadsgRRA(paste0(i,".sgrna_summary.txt")))
}

for (i in files.toPlot){
  x <- get(paste0(i,".gdata"))
  print(plot_gdata_volcano(x))
}
```

## In Vivo Pool F

```{r}
invivo.poolF.1 <- ldf.200406[[6]][c(1,11)]
invivo.poolF.2 <- ldf.200627[[42]][c(1,3,4,5,6,7,8,9,11,12)]
invivo.poolF.3 <- ldf.200627[[53]][c(1,4,5,6,8,9,10,11,12,13,25,26,27,28,29,49,50)]

invivo.poolF <- merge(x=invivo.poolF.1,y=invivo.poolF.2, by.x=c("Construct.Barcode"),by.y=c("Construct.Barcode"), all=TRUE)
invivo.poolF <- merge(x=invivo.poolF,y=invivo.poolF.3, by.x=c("Construct.Barcode"),by.y=c("Construct.Barcode"), all=TRUE)
invivo.poolF <- merge(x=invivo.poolF,y=sgRNAs.gene, by.x=c("Construct.Barcode"),by.y=c("Barcode.Sequence"), all=FALSE, all.x=TRUE)

col.viv.poolF <- colnames(invivo.poolF)
```

```{r}
# reorder columns
invivo.poolF.reorder <- invivo.poolF[,c(1,28,2,
                                14,15,17,19,
                                3,5,7,10,26,
                                21,22,23,24,25,
                                13,16,18,20,
                                4,6,8,9,11,27)]

# replace NA values with 0
invivo.poolF.reorder <- replace(invivo.poolF.reorder, is.na(invivo.poolF.reorder), 0)
# Write to table for mageck run
write_delim(invivo.poolF.reorder,file="invivo.poolF.txt", delim = '\t')
```

### results import and plotting

```{r}
files.toPlot <- list.files(pattern=glob2rx("invivo.poolF_*gene_summary.txt"), full.names=FALSE)
files.toPlot <- str_replace(files.toPlot, ".gene_summary.txt", "")
files.toPlot

for (i in files.toPlot){
  assign(paste0(i,".gdata"),ReadRRA(paste0(i,".gene_summary.txt"), score = c("lfc", "rra")[1]))
  assign(paste0(i,".sdata"),ReadsgRRA(paste0(i,".sgrna_summary.txt")))
}

for (i in files.toPlot){
  x <- get(paste0(i,".gdata"))
  print(plot_gdata_volcano(x))
}
```

# QC of selected data

There are a 2 samples that appear to have been sequenced multiple times.
It would be inappropriate to use more than one of these technical replicates in analysis so decisions need to me made about which to select.
These decisions were made based on "preSelect_" boxplots. When choice is not clear, first one was selected.
Selection will be done my simply omitting the appropriate column index from the mageck scripts. Omitted samples are:

invitro.poolA.txt - 4 - 200406.1.17 - Pool.A..1.8._hEGFRv3.CAR_ET.1.10_rep3_1360..1361..1362..1363..1406..1407..1408..1409.x
invitro.poolB.txt - 11 - 200627.63.5 - In.vitro_Pool.B..9.16._mCD19.CAR_ET.1.10_rep3_1410..1411..1412..1413..1414..1415..1416..1417.y

## QC plots of normalized data


```{r,fig.height=4,fig.width=5}
files.toPlot <- list.files(pattern=glob2rx("*all_v_input.normalized.txt"), full.names=FALSE)

# Create an empty list to store the ggplot objects
PCAdata <- list()
PCAplots <- list()

for (i in files.toPlot){
  plotTitle <- sub("_all_v_input.normalized.txt", "", i)
  norm <- read.table(i, row.names = 1, sep = "\t", header = TRUE)
  norm.l2 <- norm %>% select(-Gene)
  norm.l2 <- log2(norm.l2+1)
  dims <- dim(norm.l2)
  norm.l2 <- norm.l2 %>% rename_at(vars(everything()), ~str_replace_all(., "\\.\\.\\d+\\.\\d+\\.", "")) %>% 
    rename_at(vars(everything()), ~str_replace_all(., "_\\d{4}\\.{2}\\d{4}\\.{2}\\d{4}\\.{2}\\d{4}\\.{2}\\d{4}\\.{2}\\d{4}\\.{2}\\d{4}\\.{2}\\d{4}", "")) %>% 
    rename_at(vars(everything()), ~str_replace_all(., "In.vitro_", "")) %>% 
    rename_at(vars(everything()), ~str_replace_all(., "In.vitro\\.", "")) %>%
    rename_at(vars(everything()), ~str_replace_all(., "In.vivo_", "")) %>% 
    rename_at(vars(everything()), ~str_replace_all(., "In.vivo\\.", "")) %>% 
    #rename_at(vars(everything()), ~str_replace_all(., "^AR\\d{4}_", "")) %>% 
    rename_at(vars(everything()), ~str_replace_all(., "Pool\\.[ABCDEF]_", "")) %>% 
    rename_at(vars(everything()), ~str_replace_all(., "_Pool\\.[ABCDEF]_.", "")) %>% 
    rename_at(vars(everything()), ~str_replace_all(., "\\.Pool\\.[ABCDEF]", "")) %>% 
    rename_at(vars(everything()), ~str_replace_all(., "_Pool\\.[ABCDEF]", "")) %>% 
    rename_at(vars(everything()), ~str_replace_all(., "_rep", "_"))
  assign(paste0(plotTitle,".boxPlot"),
         ggplot(stack(norm.l2), aes(x = ind, y = values)) + geom_boxplot() + ylim(0, 12) +
           theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + 
           ggtitle(paste0(plotTitle," - ",dims[1],"x",dims[2])))
  
  select.pca <- prcomp(t(norm.l2))
  var <- select.pca$sdev^2
  variance <- var/sum(var)
  percentVar <- select.pca$sdev^2 / sum(select.pca$sdev^2 )
  percentVar <- round(100 * percentVar,2)
  select.pca$percentVar <- percentVar
  select.pca$samps <- colnames(norm.l2)
  select.pca$samps <- select.pca$samps %>% 
    str_replace_all(., "^AR\\d{4}_", "") %>% 
    str_replace_all(., "\\.[xy]$", "") %>%
    str_replace_all(., "CAR_", "") %>%
    str_replace_all(., "_[123]$", "")
  data <- as.data.frame(select.pca$x)
  data$fill <- factor(select.pca$samps)
  plot <- ggplot(data, aes(x=PC1, y=PC2)) + 
         geom_point(aes(fill = fill),shape=21, size = 4) + 
         xlab(paste0("PC1 - ",select.pca$percentVar[1]," % of variability")) + 
         ylab(paste0("PC2 - ",select.pca$percentVar[2]," % of variability")) +
    theme(legend.text = element_text(size = 8))
  PCAdata[[plotTitle]] <- data
  PCAplots[[plotTitle]] <- plot
}
```

### Assemble pairs of plots

```{r,fig.height=9,fig.width=6}
invitA <- ggarrange(invitro.poolA.boxPlot,PCAplots[[1]],nrow=2,ncol=1)
invitB <- ggarrange(invitro.poolB.boxPlot,PCAplots[[2]],nrow=2,ncol=1)
invitC <- ggarrange(invitro.poolC.boxPlot,PCAplots[[3]],nrow=2,ncol=1)
invitD <- ggarrange(invitro.poolD.boxPlot,PCAplots[[4]],nrow=2,ncol=1)
invitE <- ggarrange(invitro.poolD.boxPlot,PCAplots[[5]],nrow=2,ncol=1)
invitF <- ggarrange(invitro.poolF.boxPlot,PCAplots[[6]],nrow=2,ncol=1)

invivA <- ggarrange(invivo.poolA.boxPlot,PCAplots[[7]],nrow=2,ncol=1)
invivB <- ggarrange(invivo.poolB.boxPlot,PCAplots[[8]],nrow=2,ncol=1)
invivC <- ggarrange(invivo.poolC.boxPlot,PCAplots[[9]],nrow=2,ncol=1)
invivD <- ggarrange(invivo.poolD.boxPlot,PCAplots[[10]],nrow=2,ncol=1)
invivE <- ggarrange(invivo.poolE.boxPlot,PCAplots[[11]],nrow=2,ncol=1)
invivF <- ggarrange(invivo.poolF.boxPlot,PCAplots[[12]],nrow=2,ncol=1)

vit <- ggarrange(invitA,invitB,invitC,invitD,invitE,invitF,nrow=1,ncol=6)
viv <- ggarrange(invivA,invivB,invivC,invivD,invivE,invivF,nrow=1,ncol=6)
```

### Build final QC figures

```{r,fig.width=20,fig.height=8}
vit
viv
#ggarrange(vit,viv,nrow=1,ncol=2)
```


## Volcano plots of hart essential genes in EGFR CAR vs Input comparisons

```{r}
gdata_obj <- ls(pattern=glob2rx("*input.gdata"))
gdata_obj <- grep("all", gdata_obj, invert = TRUE, value = TRUE)
for (i in 1:length(gdata_obj)){
  print(plot_essentials(get(gdata_obj[i])) + ggtitle(gdata_obj[i]))
}
```

## Box plots of essential genes in EGFR CAR vs Input comparisons

```{r}
gdata_obj <- ls(pattern=glob2rx("*input.gdata"))
gdata_obj <- grep("all", gdata_obj, invert = TRUE, value = TRUE)

EssentialPlot.plots <- list()

for (i in 1:length(gdata_obj)){
  plotTitle <- sub(".gdata", "", gdata_obj[[i]])
  plot <- vlnplot_essentials(get(gdata_obj[i])) + ggtitle(plotTitle)
  EssentialPlot.plots[[plotTitle]] <- plot
}
```

### The essential gene boxplots are available in resulting list

```{r,fig.width=18,fig.height=6}
ggarrange(EssentialPlot.plots[[1]],EssentialPlot.plots[[2]],EssentialPlot.plots[[3]],EssentialPlot.plots[[4]],EssentialPlot.plots[[5]],EssentialPlot.plots[[6]],
          EssentialPlot.plots[[7]],EssentialPlot.plots[[8]],EssentialPlot.plots[[9]],EssentialPlot.plots[[10]],EssentialPlot.plots[[11]],EssentialPlot.plots[[12]],
          nrow=2,ncol=6)
```
## Assembling the original screen re-analysis data

```{r}
invitro.1_10.gdata.list <- ls(pattern=glob2rx("invitro.*mCD19.CAR_ET.1.10_v_hEGFRv3.CAR_ET.1.10.gdata$"))

invitro.1_10.gdata.combined <- rbind(invitro.poolA_mCD19.CAR_ET.1.10_v_hEGFRv3.CAR_ET.1.10.gdata,
                                     invitro.poolB_mCD19.CAR_ET.1.10_v_hEGFRv3.CAR_ET.1.10.gdata,
                                     invitro.poolC_mCD19.CAR_ET.1.10_v_hEGFRv3.CAR_ET.1.10.gdata,
                                     invitro.poolD_mCD19.CAR_ET.1.10_v_hEGFRv3.CAR_ET.1.10.gdata,
                                     invitro.poolE_mCD19.CAR_ET.1.10_v_hEGFRv3.CAR_ET.1.10.gdata,
                                     invitro.poolF_mCD19.CAR_ET.1.10_v_hEGFRv3.CAR_ET.1.10.gdata)

invitro.1_10.gdata.combined <- rename(invitro.1_10.gdata.combined,invitro.1_10.Score = Score, invitro.1_10.FDR = FDR)

invitro.1_2.gdata.list <- ls(pattern=glob2rx("invitro.*mCD19.CAR_ET.1.2_v_hEGFRv3.CAR_ET.1.2.gdata$"))

invitro.1_2.gdata.combined <- rbind(invitro.poolA_mCD19.CAR_ET.1.2_v_hEGFRv3.CAR_ET.1.2.gdata,
                                     invitro.poolB_mCD19.CAR_ET.1.2_v_hEGFRv3.CAR_ET.1.2.gdata,
                                     invitro.poolC_mCD19.CAR_ET.1.2_v_hEGFRv3.CAR_ET.1.2.gdata,
                                     invitro.poolD_mCD19.CAR_ET.1.2_v_hEGFRv3.CAR_ET.1.2.gdata,
                                     invitro.poolE_mCD19.CAR_ET.1.2_v_hEGFRv3.CAR_ET.1.2.gdata,
                                     invitro.poolF_mCD19.CAR_ET.1.2_v_hEGFRv3.CAR_ET.1.2.gdata)

invitro.1_2.gdata.combined <- rename(invitro.1_2.gdata.combined,invitro.1_2.Score = Score, invitro.1_2.FDR = FDR)

invivo.BM_10.gdata.list <- ls(pattern=glob2rx("invivo.*BM_mCD19_10m_v_BM_hEGFRv3_15m.gdata$"))

invivo.BM_10.gdata.combined <- rbind(invivo.poolA_BM_mCD19_10m_v_BM_hEGFRv3_15m.gdata,
                                    invivo.poolB_BM_mCD19_10m_v_BM_hEGFRv3_15m.gdata,
                                    invivo.poolC_BM_mCD19_10m_v_BM_hEGFRv3_15m.gdata,
                                    invivo.poolD_BM_mCD19_10m_v_BM_hEGFRv3_15m.gdata,
                                    invivo.poolE_BM_mCD19_10m_v_BM_hEGFRv3_15m.gdata,
                                    invivo.poolF_BM_mCD19_10m_v_BM_hEGFRv3_15m.gdata)

invivo.BM_10.gdata.combined <- rename(invivo.BM_10.gdata.combined,invivo.BM_10.Score = Score, invivo.BM_10.FDR = FDR)

invivo.BM_15.gdata.list <- ls(pattern=glob2rx("invivo.*BM_mCD19_15m_v_BM_hEGFRv3_15m.gdata$"))

invivo.BM_15.gdata.combined <- rbind(invivo.poolA_BM_mCD19_15m_v_BM_hEGFRv3_15m.gdata,
                                    invivo.poolB_BM_mCD19_15m_v_BM_hEGFRv3_15m.gdata,
                                    invivo.poolC_BM_mCD19_15m_v_BM_hEGFRv3_15m.gdata,
                                    invivo.poolD_BM_mCD19_15m_v_BM_hEGFRv3_15m.gdata,
                                    invivo.poolE_BM_mCD19_15m_v_BM_hEGFRv3_15m.gdata,
                                    invivo.poolF_BM_mCD19_15m_v_BM_hEGFRv3_15m.gdata)

invivo.BM_15.gdata.combined <- rename(invivo.BM_15.gdata.combined,invivo.BM_15.Score = Score, invivo.BM_15.FDR = FDR)

invivo.SP_10.gdata.list <- ls(pattern=glob2rx("invivo.*SP_mCD19_10m_v_SP_hEGFRv3_15m.gdata$"))

invivo.SP_10.gdata.combined <- rbind(invivo.poolA_SP_mCD19_10m_v_SP_hEGFRv3_15m.gdata,
                                    invivo.poolB_SP_mCD19_10m_v_SP_hEGFRv3_15m.gdata,
                                    invivo.poolC_SP_mCD19_10m_v_SP_hEGFRv3_15m.gdata,
                                    invivo.poolD_SP_mCD19_10m_v_SP_hEGFRv3_15m.gdata,
                                    invivo.poolE_SP_mCD19_10m_v_SP_hEGFRv3_15m.gdata,
                                    invivo.poolF_SP_mCD19_10m_v_SP_hEGFRv3_15m.gdata)

invivo.SP_10.gdata.combined <- rename(invivo.SP_10.gdata.combined,invivo.SP_10.Score = Score, invivo.SP_10.FDR = FDR)
```

## Checking combined data

```{r}
combined.list <- ls(pattern=("*gdata.combined$"))

for (i in combined.list){
  print(dim(get(i)))
}

for (i in combined.list){
  print(head(get(i)))
}
```

## Merging original screen re-analysis

```{r}
#combined.objects <- mget(combined.list)
#combined.df <- combined.objects %>% reduce(inner_join, by='gene')

geneLevel <- left_join(invitro.1_10.gdata.combined, invitro.1_2.gdata.combined, by = "id") %>%
  left_join(invivo.BM_10.gdata.combined, by = "id") %>%
  left_join(invivo.BM_15.gdata.combined, by = "id") %>%
  left_join(invivo.SP_10.gdata.combined, by = "id")
```

### Gene Level Whitelist and other annotations

```{r}
geneLevel.annotated <- merge(geneLevel,GeneSymWhitelist,by.x = 'id', by.y = 'GeneSym',all=TRUE)
geneLevel.annotated <- merge(geneLevel.annotated,biocarta.ifng,by.x = 'id', by.y = 'Gene',all=TRUE)
geneLevel.annotated <- merge(geneLevel.annotated,hallmark.ifng,by.x = 'id', by.y = 'Gene',all=TRUE)
geneLevel.annotated <- merge(geneLevel.annotated,mmKEGG.toJoin,by.x = 'id', by.y = 'MmSym',all=TRUE)
geneLevel.annotated.whitelist <- geneLevel.annotated %>% dplyr::filter(geneSym.whitelist == "Yes")

write.xlsx(geneLevel.annotated.whitelist, file="geneLevel.annotated.whitelist.xlsx", overwrite = TRUE, rowNames=TRUE)
```

# write session info

```{r}
sessionInfo()
writeLines(capture.output(sessionInfo()), "B-ALL_primaryScreen_sessionInfo.txt")
```